---
title: "COVID-19 analysis for Russia"
description: |
  Welcome to my new blog, this is the anlaysis of COVID-19 for Russia, mainly focusing on the region distribution, death rate and recovered rate. Hope it can help after you read it!
author:
  - name: Yiwen Zhang 
    url: https://thirsty-pasteur-78571a.netlify.app/
date: 09-12-2020
categories:
  - COVID-19 Russia
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false
preview: covid-Russia.png
bibliography: references.bib
biblio-style: authoryear-comp
---

# Introduction

COVID-19 virus (corona virus) has been starting to spread inside of Russia. This is important to investigate and understand the spreading from a very low level. As Russia is a very huge and heterogeneous country, for better analyze we have to consider Russia infection cases distributed by region. And we will also explore the death rate and recovered rate of some high-confirmed regions, presenting by two graphs.

# Data description

## Data source

The data is mainly collected from official government resource [@russiaofficial].And it is then cleaned by a data scientist. I download the dataset from website Kaggle. [@kapral2020] I used two .csv files to cover my data story, which contains 15 variables in total as followed.

## Data explanation

Variable       | Description
---------------|------------
Date   	       |The recorded date
Region	       |Region name in Russia
Region ID	     |Region ID
DConf	         |Daily confirmed cases
DDeath	       |Daily death cases
DRec    	     |Daily recovered cases
Conf           |The cumulative confirmed cases
Death          |The cumulative death cases
Rec     	     |The cumulative recovered cases
Latitude    	 |Latitude
LongitudeD     |Longitude 
Population     |Population in that region
Conf_rate	     |confirmed rate
Death_rate	   |death rate
Rec_rate   	   |recovered rate



# Data Analysis

In this section, I will explore the region distribution of COVID-19 in Russia, as well as the death rate and recovered rate of the top four high-confirmed regions.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(coronavirus)
library(tidyverse)
library(DT)
library(formattable)
library(plotly)
library(lubridate)
library(knitr)
library(dplyr)
library(reactable)
library(kableExtra)
library(sparkline)
library(htmltools)
library(leaflet)
library(ggplot2)
```

```{r read-data}
russia_case <- read_csv(here::here("_posts/blog2/data-Russia/covid19-russia-cases-scrf.csv"))
region_info <- read_csv(here::here("_posts/blog2/data-Russia/regions-info.csv"))
```

```{r clean-data}
#delete the column won't be used and drop NA
russia_case <- russia_case %>%
  select(-`Region/City`)

region_info_new <- region_info %>%
  select(`Region_eng`,`Latitude`,`Longitude`) 

region_pop <- region_info %>%
  select(`Region_eng`,`Population`) 
  
```

## Story 1 - Region Distribution

As a transcontinental country, Russia has the highest number of confirmed cases in Europe, the second-highest in Asia after India, and the fourth-highest in the world after the United States, India, and Brazil.[@wikipedia2020] Therefore, for such a country with a large number of confirmed cases and a vast territory, we should look at the spread and distribution of COVID-19 from a lower dimension level, which means exploring that by regions.

Map \@ref(fig:confirmed-map) shows the region distribution of COVID-19 in Russia, the region marked with a circle indicates that there are confirmed cases. And the larger the circle radius, the more confirmed cases in this area.

It can be observed that COVID-19 in Russia was centered in the city of Moscow, which accounted for the highest number of cases, measuring at over 241 thousand as of July 31, 2020. It was followed by the Moscow Region with approximately 63 thousand. In total, around 0.84 million COVID-19 cases were recorded in Russia as of that date.
                                              
On 2 March, the first case in Russia was confirmed in Moscow, and then COVID-19 spread rapidly across the country. As Moscow is the transportation center and the largest comprehensive city in Russia, the flow of people is huge and the crowd is dense, which provides conditions for the spread of the disease on a large scale, which is also one of the reasons why Moscow has become the area with the most confirmed cases. And it can be seen that the most confirmed regions followed by Moscow are not far from it in this map.

```{r rename}
#rename the column name
russia_case <- russia_case %>%
  setNames(c("Date","Region","Region_ID","DConf","DDeath","DRec","Conf","Death","Rec"))

region_info_new <- region_info_new %>%
  setNames(c("Region","Latitude","LongitudeD"))
```

```{r join-data}
#join the data
covid_location = left_join(x = russia_case, y = region_info_new, by="Region")
```


```{r confirmed-map,fig.cap="COVID-19 Region Distribution in Russia"}
#draw the map of distribution of confirmed cases
  leaflet() %>%
            #use setView() to choose the  map center and zoom level
            setView(lat = 55.50432, lng = 38.03539,  zoom = 3) %>%
            addTiles() %>%
            addCircleMarkers(
                data = covid_location,
                # set layer-Id to get id in click event
                layerId = ~Region, 
                lng = ~LongitudeD,
                lat = ~Latitude,
                radius = ~(Conf/2100), # to scale down
                label = ~Region, #  show label name when mouse hovers
                weight = 1
            )
```

## Story 2 - Death rate and Recovered rate

In this part, I would focus on the death rate and recovered rate in some regions. Considering the large number of regions, I chose the top four regions with the largest cumulative confirmed rates (per 10,000 population) as the analysis objects. I think it is more representative, because such areas often have the best medical conditions in Russia, from which  we can also have a glimpse of Russia's treatment of the COVID-19. And Table \@ref(fig:table2) shows these top four regions. They are Yamalo-Nenets Autonomous Okrug, Moscow, Tyva Republic and Murmansk region.

```{r  mutate-data}
region_pop<- region_pop %>%
  setNames(c("Region","Population"))

 # Identify the top four confirmed rate areas on the last recorded day
covid_rate = left_join(x = russia_case, y = region_pop, by="Region") %>%
  mutate(Conf_rate = (Conf/Population)*100000) %>%
  mutate(Death_rate = (Death/Population)*100000) %>%
  mutate(Rec_rate = (Rec/Population)*100000)

covid_top_rate <- covid_rate %>%
  filter(Date == "2020-07-31") %>%
  arrange(desc(Conf_rate)) %>%
  head(4)
```

```{r table2,fig.cap="Rate of top four areas per 100 thousand people"}
datatable(covid_top_rate, 
          escape = FALSE,
          caption = htmltools::tags$caption( style = 'caption-side: top; text-align: center; color:purple; padding-bottom: 20px; font-size:190% ;','Rate of top four areas per 100 thousand people'),
          options = list(paging = FALSE, 
                         dom = "t",
                         scrollX = T,
                         columnDefs = list(list(className = 'dt-center')),
                         fnDrawCallback = htmlwidgets::JS(
 "function(settings, json) {",
    "HTMLWidgets.staticRender();" ,
    "$(this.api().table().header()).css({'font-size': '15px', 'background-color': '#c2d1f0', 'color': '#fff'});",
    "$(this.api().columns().data()).css({'font-size': '5px'});",

    "$(this.api().tables().body()).css({'font-size': '12px'});",
 
    "}"
)
       )) %>%
  spk_add_deps() 

```


So, I draw line graphs for these four regions as Figure \@ref(fig:topfourrate). It can be observed that all these regions have quite low death rates which are close to zero. Why are not death rates rising with case numbers? It is likely that among the steadily rising number of people who have tested positive for the disease, an increasing proportion are young and a declining proportion are older, so that having the disease is dramatically less lethal for each person with it.[@coviddeathrate]

As for the recovered rate, all these four show upward trends, which shows that the overall cure trend is good. To be more detail, the cure rate of Yamalo-Nenets Autonomous Okrug shows a rapid increase. It is easy to understand that the number of cured people will increase the most with the time because of the large number of infected people. And the slope of this curve is also the largest, which also shows that the growth rate of cure cases is the largest, indicating that the medical conditions in this region are quite ideal. 

However, Moscow has the most population, and the growth rate of recovered cases is getting gradually decreased. Due to the reducing of daily confirmed cases, the daily recovered cases have also decreased. And that is why the cure rate curve in Moscow becomes more and more gentle.


```{r filter-data}
# filter top four confirmed rate areas' data

covid_rate_top4 <- covid_rate %>%
  filter(Region == c("Yamalo-Nenets Autonomous Okrug","Moscow","Tyva Republic","Murmansk region"))
```

```{r topfourrate, fig.cap="Death and Recovered rate per 100,000 population (4 regions)"}
p2 <- covid_rate_top4 %>%
  ggplot(aes(x = Date,
             group = Region)) +
  geom_line(aes(y = Death_rate, color = "death rate"))+
  geom_line(aes(y = Rec_rate, color = "recovered rate")) +
  facet_wrap(~Region) +
  ggtitle("Death and Recovered rate per 100,000 population (4 regions)") + 
  ylab("Rate") +
  theme(#axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

ggplotly(p2)
```


# Conclusion

General speaking, the coronavirus is widely distributed in Russia, but it is mainly concentrated in several regions with Moscow as the center. In terms of disease control and cure, the mortality rate remained at a very low level, while the cure rate showed a continuously rising trend, indicating that although the epidemic situation in Russia was severe, the anti-epidemic achievements were great.


# Acknowledgments

Thanks for the providers of these packages used as follows:


- plotly [@plotly]

- tidyverse [@tidyverse]

- lubridate [@lubridate] 

- kableExtra [@kableExtra]

- DT [@DT]

- dplyr [@dplyr]

- knitr [@knitr]

- formattable [@formattable]

- reactable [@reactable]

- coronavirus [@coronavirus]

- sparkline [@sparkline]

- htmltools[@htmltools]

- ggplot2[@ggplot2]

- leaflet[@leaflet]
