---
title: "COVID-19 analysis for Russia"
description: |
  Welcome to my new blog, this is the anlaysis of COVID-19 for Russia, mainly focusing on exploring case numbers. Hope you can enjoy reading what I share and display!
author:
  - name: Yiwen Zhang 
    url: https://thirsty-pasteur-78571a.netlify.app/
date: 09-03-2020
categories:
  - COVID-19 Ghana
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false
preview: covid-Russia.png
bibliography: references.bib
biblio-style: authoryear-comp
---

# Introduction

COVID-19 virus (corona virus) has been starting to spread inside of Russia. This is important to investigate and understand the spreading from a very low level. As Russia is a very huge and heterogeneous country, for better analyze we have to consider Russia infection cases distributed by region. And we will also explore the death rate and recovered rate of some high-confirmed regions, presenting by two graphs.

# Data description

## Data source

## Data explanation

Variable       | Description
---------------|------------
Date   	       |The recorded date
Region	       |Region name in Russia
Region ID	     |Region ID
DConf	         |Daily confirmed cases
DDeath	       |Daily death cases
DRec    	     |Daily recovered cases
Conf           |The cumulative confirmed cases
Death          |The cumulative death cases
Rec     	     |The cumulative recovered cases
Latitude    	 |Latitude
LongitudeD     |Longitude 
Population     |Population in that region
Conf_rate	     |confirmed rate
Death_rate	   |death rate
Rec_rate   	   |recovered rate



# Data Analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(coronavirus)
library(tidyverse)
library(DT)
library(formattable)
library(plotly)
library(lubridate)
library(knitr)
library(dplyr)
library(reactable)
library(kableExtra)
library(sparkline)
library(htmltools)
library(leaflet)
library(ggplot2)
```

```{r}
russia_case <- read_csv(here::here("_posts/blog2/data-Russia/covid19-russia-cases-scrf.csv"))
region_info <- read_csv(here::here("_posts/blog2/data-Russia/regions-info.csv"))
```

```{r}
#delete the column won't be used and drop NA
russia_case <- russia_case %>%
  select(-`Region/City`)

region_info_new <- region_info %>%
  select(`Region_eng`,`Latitude`,`Longitude`) 

region_pop <- region_info %>%
  select(`Region_eng`,`Population`) 
  
```

## Story 1

```{r}
#rename the column name
russia_case <- russia_case %>%
  setNames(c("Date","Region","Region_ID","DConf","DDeath","DRec","Conf","Death","Rec"))

region_info_new <- region_info_new %>%
  setNames(c("Region","Latitude","LongitudeD"))
```

```{r}
#join the data
covid_location = left_join(x = russia_case, y = region_info_new, by="Region")
```


```{r confirmed-data}
#draw the map of distribution of confirmed cases
  leaflet() %>%
            #use setView() to choose the  map center and zoom level
            setView(lat = 55.50432, lng = 38.03539,  zoom = 3) %>%
            addTiles() %>%
            addCircleMarkers(
                data = covid_location,
                # set layer-Id to get id in click event
                layerId = ~Region, 
                lng = ~LongitudeD,
                lat = ~Latitude,
                radius = ~(Conf/2100), # to scale down
                label = ~Region, #  show label name when mouse hovers
                weight = 1
            )
```

## Story 2

```{r}
region_pop<- region_pop %>%
  setNames(c("Region","Population"))

 # Identify the top four confirmed rate areas on the last recorded day
covid_rate = left_join(x = russia_case, y = region_pop, by="Region") %>%
  mutate(Conf_rate = (Conf/Population)*100000) %>%
  mutate(Death_rate = (Death/Population)*100000) %>%
  mutate(Rec_rate = (Rec/Population)*100000)

covid_top_rate <- covid_rate %>%
  filter(Date == "2020-07-31") %>%
  arrange(desc(Conf_rate)) %>%
  head(4)
```

```{r interactive,fig.cap="Rate of top four areas per 100 thousand people"}
datatable(covid_top_rate, 
          escape = FALSE,
          caption = htmltools::tags$caption( style = 'caption-side: top; text-align: center; color:purple; padding-bottom: 20px; font-size:190% ;','Rate of top four areas per 100 thousand people'),
          options = list(paging = FALSE, 
                         dom = "t",
                         scrollX = T,
                         columnDefs = list(list(className = 'dt-center')),
                         fnDrawCallback = htmlwidgets::JS(
 "function(settings, json) {",
    "HTMLWidgets.staticRender();" ,
    "$(this.api().table().header()).css({'font-size': '15px', 'background-color': '#c2d1f0', 'color': '#fff'});",
    "$(this.api().columns().data()).css({'font-size': '5px'});",

    "$(this.api().tables().body()).css({'font-size': '12px'});",
 
    "}"
)
       )) %>%
  spk_add_deps() 

```

```{r}
# filter top four confirmed rate areas' data

covid_rate_top4 <- covid_rate %>%
  filter(Region == c("Yamalo-Nenets Autonomous Okrug","Moscow","Tyva Republic","Murmansk region"))
```

```{r topfourrate, fig.cap="Confirmed rate of top four areas per 100 thousand people"}
p2 <- covid_rate_top4 %>%
  ggplot(aes(x = Date,
             group = Region)) +
  geom_line(aes(y = Death_rate, color = "death rate"))+
  geom_line(aes(y = Rec_rate, color = "recovered rate")) +
  facet_wrap(~Region) +
  ggtitle("Confirmed rate of top four areas per 100 thousand people") + 
  ylab("Rate") +
  theme(#axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

ggplotly(p2)
```

# Conclusion

Generally speaking, the situation of COVID-19 in Ghana presents a trend of normal development and ideal control with a quite low level death cases and balanced situation between confirmed cases and recovered cases. However, with the cumulative increase of confirmed cases and the influence of neighboring countries, the ability of the country’s health system will also face a crisis, so both individuals and the whole society of Ghana should still take it seriously.


# Acknowledgments

Thanks for the providers of these packages used as follows:


- plotly [@plotly]

- tidyverse [@tidyverse]

- lubridate [@lubridate] 

- kableExtra [@kableExtra]

- DT [@DT]

- dplyr [@dplyr]

- knitr [@knitr]

- formattable [@formattable]

- reactable [@reactable]

- coronavirus [@coronavirus]

- sparkline [@sparkline]

- htmltools[@htmltools]

- ggplot2[@ggplot2]

- leaflet[@leaflet]
